---
title: "README"
author: "Bob Rudis"
date: August 22, 2014
output:
  md_document:
    variant: markdown_github
---

The `dtupdate` packages has functions that attempt to figure out which packages have non-CRAN versions (currently only looks for github ones) and then tries to figure out which ones have updates (i.e. the github version is > local version). It provides an option (not recommended) to auto-update any packages with newer development versions, which is tempered by the ability to selectively install said packages.

The `URL` and `BugReports` fields are, frankly, a mess. Many packages have multiple URLs in one or both of those fields and the non-github URLs are all over the place in terms of formatting. It will take some time, but I'm pretty confident I can get r-forge, bitbucket, gitorius and other external repos working. This was an easy first step.

The following functions are implemented:

- `github_update` - find, report and optionally update packages installed from or available on github. This initial version just keys off of the `BugReports:` field, looking for a github-ish URL and then grabbing what info that it can to see if the repo is in package format and has a `DESCRIPTION` file it can key off of

### News

- Version `1.1` incorporates functionality from [Thomas J Leeper](http://twitter.com/thosjleeper)'s \code{#spiffy} gist: \url{https://gist.github.com/leeper/9123584}, including the ability to interactively select which packages to install, the option to specify which `libLoc` will be searched by `installed.packages` and handling of a fringe case where the repo name does not match the package name (ironically, this was due to Hadley's `reshape` repo for the `reshape2` package)
- Version `1.0` released (nascent github pkg update capability)

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/dtupdate")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(dtupdate)

# current verison
packageVersion("dtupdate")

# see what packages are available for an update
github_update()

```

### Test Results

```{r}
library(dtupdate)
library(testthat)

date()

test_dir("tests/")
```

